---
title: "R Markdown and plotly"
author: "Nikolaos Perdikis"
date: "27 8 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Import the data

The source of the data is the latest unemployment survey of the European Statistics organization, Eurostat.  
   
The link to the exact statistic is  [here](https://ec.europa.eu/eurostat/databrowser/view/tps00203/default/table?lang=en) (link opens browser to Eurostat website)

Both the CSV extracted from their website (simplified) and the code of this presentation can be found in the repository: https://github.com/NikolasPerdikis/np_plotly  

**Data last update: 01/08/2019 23:00**

```{r load_library,echo=F,results='hide',message=F,warning=F}
library(plotly)
library(tidyr)
library(dplyr)

# EUROSTAT
# Source: https://ec.europa.eu/eurostat/databrowser/view/tps00203/default/table?lang=en
# Code: TPS00203   last update: 01/08/2019 23:00   

tps_00203_csv <- "D:/Github/np_plotly/tps_00203.csv"
tps_00203 <- read.csv(tps_00203_csv,header=FALSE,sep=",",col.names=c("cname","tps00203"),na.strings = ":")

```

## Unemployment in Europe
### Percentage Unemployed of Active Population (15-74)
### (Eurostat, 2018)  

```{r graph, warning=F,message=F}

#Sys.setenv('MAPBOX_TOKEN'='pk.eyJ1IjoibnBlciIsImEiOiJjanp0aTYxZHkwMmIyM2NvYTZ0cnQycHNxIn0.OxDGGkBF4MeTiZhwHJpdbA')

library(plotly)

trace1 <- list(
  geo = "geo", 
  type = "choropleth", 
  z = tps_00203$tps00203, 
  showscale = TRUE, 
  locationmode = "country names", 
  locations = tps_00203$cname,
  autocolorscale = TRUE
)
data <- list(trace1)


layout <- list(
  geo = list(
    scope = "europe", 
    domain = list(
      x = c(0, 1), 
      y = c(0, 1)
    ), 
    lataxis = list(range = c(35.0, 70.0)), 
    lonaxis = list(range = c(-9.0, 38.0)), 
    showland = TRUE, 
    landcolor = "rgb(229, 229, 229)", 
    showframe = TRUE, 
    projection = list(type = "Mercator"), 
    resolution = 50, 
    countrycolor = "rgb(255, 0, 255)", 
    coastlinecolor = "rgb(128, 128, 128)", 
    showcoastlines = TRUE
  ), 
  title = "Hover mouse over country to see name and rate", 
  legend = list(traceorder = "reversed")
)
p <- plot_ly()
p <- add_trace(p, geo=trace1$geo, type=trace1$type, z=trace1$z, showscale=trace1$showscale, locationmode=trace1$locationmode, locations=trace1$locations, autocolorscale=trace1$autocolorscale)
p <- layout(p, geo=layout$geo, title=layout$title, legend=layout$legend)
p
```

## Thank you!